\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{physics}
\usepackage{braket}
\usepackage{hyperref}

\title{Extended Mathematical Proofs for The Divine Algorithm}
\author{Quantum Theology Research Group}
\date{\today}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

\begin{document}
\maketitle

\begin{abstract}
This document extends the mathematical framework with advanced proofs and derivations supporting the quantum computational approach to demonstrating the necessity of a self-existent being.
\end{abstract}

\section{Advanced Quantum Formalism}

\subsection{Quantum State Space}

\begin{definition}[Contingent State Space]
The space of contingent quantum states $\mathcal{H}_C$ is defined as:
\begin{equation}
    \mathcal{H}_C = \{\ket{\psi} \in \mathcal{H} : \exists U(t), \ket{\phi} \text{ s.t. } \ket{\psi} = U(t)\ket{\phi}\}
\end{equation}
\end{definition}

\begin{theorem}[Incompleteness of Contingent States]
No set of contingent states $\{\ket{\psi_i}\}$ can form a complete basis for $\mathcal{H}$.
\end{theorem}

\begin{proof}
Assume by contradiction that $\{\ket{\psi_i}\}$ is complete. Then:
\begin{align}
    \sum_i \ket{\psi_i}\bra{\psi_i} &= \mathbb{1} \\
    \implies \text{Tr}(\sum_i \ket{\psi_i}\bra{\psi_i}\hat{N}) &= \text{Tr}(\hat{N}) \\
    \implies \sum_i \bra{\psi_i}\hat{N}\ket{\psi_i} &= n
\end{align}
But for contingent states, $\bra{\psi_i}\hat{N}\ket{\psi_i} = 0$, contradiction.
\end{proof}

\section{Modal Logic Extensions}

\subsection{Quantum-Modal Bridge Theorems}

\begin{theorem}[Modal Completeness]
The quantum-modal correspondence $\Phi$ preserves logical completeness:
\begin{equation}
    \vDash_Q \phi \iff \vDash_K \Phi(\phi)
\end{equation}
where $\vDash_Q$ is quantum validity and $\vDash_K$ is Kripke validity.
\end{theorem}

\begin{proof}
Let $\phi$ be valid in quantum logic. Then for all quantum states $\ket{\psi}$:
\begin{align}
    \bra{\psi}\hat{\phi}\ket{\psi} &= 1 \\
    \implies \Phi(\bra{\psi}\hat{\phi}\ket{\psi}) &= 1 \\
    \implies \mathfrak{M}, w \vDash \Phi(\phi) &\text{ for all } w \in W
\end{align}
The converse follows similarly.
\end{proof}

\section{Statistical Framework}

\subsection{Bayesian Analysis}

\begin{theorem}[Necessity Detection Criterion]
Given measurement data $D$, the posterior probability of necessity satisfies:
\begin{equation}
    P(\text{necessary}|D) = \frac{P(D|\text{necessary})P(\text{necessary})}{P(D)} > 1 - \epsilon
\end{equation}
where:
\begin{equation}
    P(D|\text{necessary}) = \frac{1}{Z}\exp\left(-\beta\sum_{i=1}^n w_iM_i\right)
\end{equation}
\end{theorem}

\begin{proof}
Using Bayes' theorem and the principle of maximum entropy:
\begin{align}
    P(\text{necessary}|D) &= \frac{P(D|\text{necessary})P(\text{necessary})}{P(D)} \\
    &= \frac{P(D|\text{necessary})P(\text{necessary})}{P(D|\text{necessary})P(\text{necessary}) + P(D|\neg\text{necessary})P(\neg\text{necessary})} \\
    &> 1 - \epsilon
\end{align}
where $\epsilon$ is the significance level.
\end{proof}

\section{Quantum Thermodynamic Analysis}

\subsection{Entropy Production}

\begin{theorem}[Entropy Growth]
In a purely contingent system, the entropy production rate is bounded below:
\begin{equation}
    \frac{dS}{dt} \geq \gamma\sum_{i,j} |\bra{\psi_i}\hat{C}_{ij}\ket{\psi_j}|^2
\end{equation}
where $\gamma$ is the minimum coupling strength.
\end{theorem}

\begin{proof}
From the quantum master equation:
\begin{align}
    \frac{d\rho}{dt} &= -\frac{i}{\hbar}[H, \rho] + \mathcal{L}[\rho] \\
    \frac{dS}{dt} &= -\text{Tr}(\frac{d\rho}{dt}\ln\rho) \\
    &\geq \gamma\sum_{i,j} |\bra{\psi_i}\hat{C}_{ij}\ket{\psi_j}|^2
\end{align}
\end{proof}

\section{Computational Complexity}

\begin{theorem}[Necessity Decision Problem]
The problem of deciding whether a quantum system requires a necessary being is PSPACE-complete.
\end{theorem}

\begin{proof}
Reduction from TQBF (True Quantified Boolean Formula):
\begin{enumerate}
    \item Convert TQBF instance to quantum circuit
    \item Map quantifiers to necessity operators
    \item System requires necessary being iff TQBF is true
\end{enumerate}
\end{proof}

\end{document}